Parallel Solving of Multiple Information-Coordinated Global Optimization Problems

### 2021-03-06 2020/JPDC_MCO/2020_JPDC.tex
1

	\State
	\begin{equation}\label{eq:22}
     stop = (x_t - x_{t-1})^{1/N} \leq \varepsilon.
  \end{equation}
  \If{ \textbf{not} $stop$}
	  \State Calculate $z^{k+1} = f( y(x^{k+1}))$;
    \State Insert $(x^{k+1}, y(x^{k+1}), z^{k+1})$ into the search information $A_k$;
    \State Increase $k = k + 1$;
  \EndIf
\EndWhile
\State Find the estimate of the global minimum point
\begin{equation}\label{eq:23}
y_k^*= y(x_l),  z_k^*=z_l,
\end{equation}
where $l= \argmin_{1 \leq i \leq k}z_i$.
\State \textbf{return} $y_k^*$, $z_k^*$, $k$;
\end{algorithmic}
\end{algorithm}

@@

An obvious way to apply parallel computing is to solve the problems of the set $F$ in parallel. Undoubtedly this approach is straightforward and does not require any additional efforts to be  implemented. In this case, if a sufficient number of computational devices ({cores / processors}) is available, the time needed to solve all problems from the set $F$ will be determined by the time used in solving the most time-consuming problem. However, this time may turn out to be quite long and necessitate the use of parallel computing to solve even one global optimization problem. However, well-known and widely used parallelization methods are poorly applicable in the case of global optimization problems. For example, the search domain distribution between processors for global optimization problems leads to the global minimum of the problems to be solved being located on only one of the processors, and all other processors will perform redundant calculations.

>>>>

	\State Calculate the stop condition
	\begin{equation}\label{eq:22}
     stop = \begin{cases} true, &(x_t - x_{t-1})^{1/N} \leq \varepsilon,\\
		                      false,&(x_t - x_{t-1})^{1/N} > \varepsilon.
							\end{cases}		
  \end{equation}
  \If{ \textbf{not} $stop$}
	  \State Calculate $z^{k+1} = f( y(x^{k+1}))$;
    \State Insert $(x^{k+1}, y(x^{k+1}), z^{k+1})$ into the search information $A_k$;
    \State Increase $k = k + 1$;
  \EndIf
\EndWhile
\State Find the estimate of the global minimum point
\begin{equation}\label{eq:23}
y_k^*= y(x_l),  z_k^*=z_l,
\end{equation}
where $l= \argmin_{1 \leq i \leq k}z_i$.
\State \textbf{return} $y_k^*$, $z_k^*$, $k$;
\end{algorithmic}
\end{algorithm}

@@

An obvious way to apply parallel computing is to solve the problems of the set $F$ in parallel. Undoubtedly this approach is straightforward and does not require any additional efforts to be  implemented. In this case, if a sufficient number of computational devices ({cores/processors}) is available, the time needed to solve all problems from the set $F$ will be determined by the time used in solving the most time-consuming problem. However, this time may turn out to be quite long and necessitate the use of parallel computing to solve even one global optimization problem. However, well-known and widely used parallelization methods are poorly applicable in the case of global optimization problems. For example, the search domain distribution between processors for global optimization problems leads to the global minimum of the problems to be solved being located on only one of the processors, and all other processors will perform redundant calculations.
